Twists of supersymmetric gauge theories

### 2020-01-15 paper.tex
Editing through S2

\begin{table}[!h]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_16}
\end{table}

\begin{table}[htbp]
 \centering
 \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
 \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
 &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
 \label{table_of_twists_16}
\end{table}

@@

\subsubsection{Generalized BF theory} \label{gen_BF_section}

@@

Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
where we denote the two fields by $A$ and $B$. The BV action is
\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.

@@

\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.

@@

\section{Supersymmetry} \label{sec: susy}

In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.

\subsection{Supersymmetry algebras}

Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+, S_-$.
\end{itemize}

\begin{definition}
A \defterm{spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
\end{definition}

@@

For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation. In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
\begin{itemize}
\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.

@@

Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.

@@

\subsection{Composition algebras and Minimal Supersymmetry}
\label{sect:compositionalgebras}

We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow \cite{BaezHuerta}.

@@

It is known \cite[Chapter 1.3]{SpringerVeldkamp} that the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e. $A_\RR$ is a real composition algebra.

@@

Consider two spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
given, respectively, by
\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]

@@

\subsection{Two-dimensional chiral supersymmetry}

@@

\subsection{Supersymmetric twisting}

@@

\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
\end{itemize}

In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge. The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}. In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
\begin{itemize}
\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges. Dashed border denotes chiral supersymmetry (i.e. $(\cN_+, 0)$ in even dimensions).

\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.

\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.

\item Arrows denote compactifications from higher to lower dimensions.
\end{itemize}

@@

Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
Recall, this means we have a Maurer-Cartan element 
\[
I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
\]
where $I_{\fA}^{(k)} : \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
Define
\[
I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
\]
Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.

\begin{definition} \label{def:twisting}
Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum. The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
\end{definition}

\begin{prop}
The collection $\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
\end{prop}

@@

Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
The operator 
\end{proof}

@@

Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.  This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.  We have a natural embedding
\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
\[G_W = G_V\times \Spin(W^\perp_\RR).\]
This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.

@@

\subsection{A-Type Twists} \label{A_twist_section}
\chris{I think we should discuss these Hodge families somewhere, maybe not here though.}

%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE

% \begin{landscape}
% \begin{figure}
% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
% \node (825) [right=of 82] {};
% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
% 
% \draw[arrow] (101) -- (91);
% \draw[arrow] (91) -- (81);
% \draw[arrow] (91) -- (82);
% \draw[arrow] (81) -- (71);
% \draw[arrow] (82) -- (71);
% \draw[arrow] (82) -- (72);
% \draw[arrow] (83) -- (73);
% \draw[arrow] (71) -- (61);
% \draw[arrow] (71) -- (62);
% \draw[arrow] (72) -- (62);
% \draw[arrow] (72) -- (63);
% \draw[arrow] (73) -- (65);
% \draw[arrow] (61) -- (51);
% \draw[arrow] (62) -- (51);
% \draw[arrow] (62) -- (52);
% \draw[arrow] (63) -- (53);
% \draw[arrow] (64) -- (52);
% \draw[arrow] (64) -- (54);
% \draw[arrow] (65) -- (54);
% \draw[arrow] (51) -- (41);
% \draw[arrow] (51) -- (42);
% \draw[arrow] (52) -- (42);
% \draw[arrow] (52) -- (43);
% \draw[arrow] (53) -- (43);
% \draw[arrow] (54) -- (43);
% \draw[arrow] (54) -- (44);
% \draw[arrow] (54) -- (45);
% \draw[arrow] (41) -- (31);
% \draw[arrow] (42) -- (31);
% \draw[arrow] (42) -- (32);
% \draw[arrow] (43) -- (32);
% \draw[arrow] (44) -- (32);
% \draw[arrow] (45) -- (32);
% \draw[arrow] (31) -- (21);
% \draw[arrow] (31) -- (22);
% \draw[arrow] (32) -- (22);
% 
% \node (2d) [dimension, left=of 21] {2d};
% \node (3d) [dimension, above=of 2d] {3d};
% \node (4d) [dimension, above=of 3d] {4d};
% \node (5d) [dimension, above=of 4d] {5d};
% \node (6d) [dimension, above=of 5d] {6d};
% \node (7d) [dimension, above=of 6d] {7d};
% \node (8d) [dimension, above=of 7d] {8d};
% \node (9d) [dimension, above=of 8d] {9d};
% \node (10d) [dimension, above=of 9d] {10d};
% \end{tikzpicture}
% \caption{Orbits of square-zero supercharges.}
% \label{fig:superchargeorbits}
% \end{figure}
% \end{landscape}

\section{Supersymmetric Yang--Mills theories}

@@

\subsection{Pure super Yang--Mills theory}
\label{sect:gaugemultipletSUSY}

@@

\subsection{Matter multiplet}
\label{sect:mattermultipletSUSY}

@@

\begin{remark}
A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e. comes from a 10d square zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
\end{remark}

@@

On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.  This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.

@@

\vspace{-10pt}
\paragraph{Twisting data:}
Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
The only square zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.  Without loss of generality we will twist with respect to a supercharge of the form $Q = q_+ \otimes w_1 \in S_+ \otimes W_+$.

>>>>

\begin{table}[!h]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_8}
\end{table}

\begin{table}[htbp]
 \centering
 \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
 \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
 &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
 \label{table_of_twists_4}
\end{table}

@@

\subsubsection{Generalized BF Theory} \label{gen_BF_section}

@@

Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*,\]
\chris{I changed a shift here which I don't think was correct, but someone should double check.} where we denote the two fields by $A$ and $B$. The BV action is
\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.

@@

Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.  In order to remain within the world of perturbation theory, we will study these theories as deformations families parameterized by a complex parameter $t$.  So at $t=0$ we will recover generalized BF theory.

We will refer to these families as Hodge deformations of generalized BF theory.  The terminology here comes from Simpson's Hodge stack \chris{ref}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.

\begin{definition} \label{Hodge_family_def}
Consider the generalized BF theory on $X \times Y \times M$ associated to the $L_\infty$ algebra $\fg$, and supposed $\fg$ is equipped with a non-degenerate pairing.  The \emph{Hodge deformation} of this generalized BF theory is the $\CC[t]$ family of classical BV theories on $X \times Y \times M$, with $(E_t, \omega_t, I_t) = (E_{\mr{BF}}, \omega_{\mr{BF}}, I_{\mr{BF}})$ the same data as for generalized BF theory, so 
\[E_t = \left(\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \right)\oplus \left(\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\right),\]
but $Q_{\mr{BV},t} = Q_{\text{BV,BF}} + tQ'$, where $Q'$ is the isomorphism
\[Q' \colon \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \to 
\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\]
induced by the Calabi-Yau structure on $X$ and the non-degenerate pairing on $\fg$. 
\end{definition}

Using our mapping stack terminology, we will refer to the Hodge deformation of generalized BF theory as
\[\mr{Map}(X \times Y_{\mr{Dol}} \times M_{\mr{dR}}, B\gg_{\mr{Hod}}).\]

\subsubsection{Generalized Chern--Simons Theory} \label{gen_CS_section}
The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.

@@

\section{Supersymmetry} \label{sec: susy}
Having set up the formalism behind classical field theories in the BV and BRST formalisms, we will introduce the other main formal ingredient of this paper: the supersymmetry action.  So, we will discuss the classification of supersymmetry algebras, the notion of a supersymmetric field theory, and the idea of a \emph{twist} of a supersymmetric field theory, extending work of the first two authors in \cite{ElliottSafronov}.  We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sec:SYM} below.

\subsection{Supersymmetry Algebras} \label{sec:susyalgebras}
In this section we will recall the framework for supersymmetry algebras and their classification following Deligne \cite{DeligneSpinors} and our previous work \cite{ElliottSafronov}, we refer there for more details.

Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and let $V=V_\RR\otimes_\RR\CC$ be its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+$ and $S_-$.
\end{itemize}

\begin{definition}
A \defterm{spinorial representation} $\Sigma$ is a finite sum of spin or semi-spin representations of $\so(V)$.
\end{definition}

@@

For a given spinorial representation, the pairing $\Gamma$ is typically unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation. In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows.
\begin{itemize}
\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.

@@

We will now define the fundamental notion of a supersymmetric field theory.  Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.

@@

\subsection{Composition Algebras and Minimal Supersymmetry}
\label{sect:compositionalgebras}

We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow that of Baez and Huerta \cite{BaezHuerta}.

@@

In fact, the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e. $A_\RR$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.

@@

Consider two isomorphic spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$; we will equip the sum of these representations with an action of the Clifford algebra.  The action on the two summands $\Sigma$ and $\Sigma^*$ will be different, hence the different notation.  We define action maps
\[\rho \colon V \otimes \Sigma\rightarrow \Sigma^*,\qquad \rho \colon V\otimes \Sigma^*\rightarrow \Sigma\]
given, respectively, by
\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]

@@

\subsection{Two-dimensional Chiral Supersymmetry}

@@

\subsection{Supersymmetric Twisting}
The idea of twisting, originally developed by Witten \chris{refs}, is \chris{todo: brief contextual remarks, not much detail, as we'll say more in the intro.}

@@

\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.

\item A supercharge $Q$ is \defterm{minimal} if $n$ is odd and $d=(n+1)/2$.
\end{itemize}

In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge. The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}. In particular, the orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}.

We will now define the twist of a supersymmetric field theory by a square-zero supercharge.  In order to obtain a $\ZZ$-graded theory, we will need to also include an additional piece of data as follows.

@@

Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
Recall from Section \ref{symmetry_section} that this means we have a Maurer-Cartan element 
\[
I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
\]
where $I_{\fA}^{(k)} \colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
Define
\[
I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
\]
Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.

\begin{definition} \label{def:twisting}
Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum. The {$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{I_{\fA}^2(Q), -\}, \omega, I + I_{\fA}^{\ge 3}(Q))$, where
\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
\end{definition}

\begin{prop}
The collection $\left(E^Q, Q_{\mr{BV}} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
\end{prop}

@@

Ellipticity of $(E^Q, \d + \{I_\fA^2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
The operator 
\end{proof}

@@

Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.  This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.  We have a natural embedding
\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
\[G_W = G_V\times \Spin(W^\perp_\RR).\]
This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ \chris{we never actually defined supersymmetry algebras or R-symmetry: need to go back and add this to Section \ref{sec:susyalgebras}.}.

@@

\section{Supersymmetric Yang--Mills theories} \label{sec:SYM}

@@

\subsection{Pure Super Yang--Mills Theory}
\label{sect:gaugemultipletSUSY}

@@

\subsection{Coupling to Matter Multiplets}
\label{sect:mattermultipletSUSY}

@@

\begin{remark}
A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e. comes from a 10d square-zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
\end{remark}

@@

On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.  This will be our first example of an twist which is perturbatively trivial on its own, but non-trivial as a one-parameter family, as we discussed at the end of Section \ref{gen_BF_section}.  That is, we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.

@@

\vspace{-10pt}
\paragraph{Twisting data:}
Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.  Without loss of generality we will twist with respect to a supercharge of the form $Q = q_+ \otimes w_1 \in S_+ \otimes W_+$.
